draftFiguresPaper

### 2025-10-23 draftFiguresPaper.Rmd
fix dataset

@@

library(rnaturalearth)

# .
# .
# .

write.csv(summaryDataset, "output/datasetPlots.csv", row.names = F)

>>>>

# 2) get total papers by country
papers_by_country <- datasetClassificationCountries_long_clean %>%
  group_by(iso3, .drop = F) %>% 
  count(iso3, name = "n_papers") %>%
  arrange(desc(n_papers)) %>% 
  merge(., incomeGroups, by.x = "iso3", by.y = "Code", all.x = T, all.y = F)

@@

library(rnaturalearth)
library(terra)

world_countries_df <- as.data.frame(world_countries)

world_countries_df$iso_a3 <- ifelse(world_countries_df$iso_a3_eh == "FRA", "FRA",
                                    ifelse(world_countries_df$iso_a3_eh == "NOR", "NOR", world_countries_df$iso_a3))

summaryDataset2 <- merge(summaryDataset, world_countries_df %>% 
                          select(continent, region_un, iso_a3), by.x = "iso3", by.y = "iso_a3", all.x = T, all.y = F)

write.csv(summaryDataset2, "output/datasetPlots.csv", row.names = F)
